Exercise I
The data for the exercises is available in the attached  EconomistData.csv file. Read it in with

library(readr)
dat <- read_csv("dataSets/EconomistData.csv")
Original sources for these data are http://www.transparency.org/content/download/64476/1031428 http://hdrstats.undp.org/en/indicators/display_cf_xls_indicator.cfm?indicator_id=103106&lang=en

These data consist of Human Development Index and Corruption Perception Index scores for several countries.

1. Create a scatter plot with CPI on the x axis and HDI on the y axis.

```{r}
library(readr) 
data <- read_csv("EconomistData.csv")
library(tidyverse)
ggplot(data, aes(x=CPI,y=HDI)) +geom_point()
```

2. Color the points blue.

```{r}
ggplot(data, aes(x=CPI,y=HDI)) +geom_point(color="blue")
```


3. Map the color of the the points to Region.

```{r}
ggplot(data, aes(x=CPI,y=HDI, color=Region)) +geom_point()
```


4. Make the points bigger by setting size to 2
```{r}
ggplot(data, aes(x=CPI,y=HDI, color=Region, size=2)) + geom_point()
```

5. Map the size of the points to HDI.Rank
```{r}
ggplot(data, aes(x = CPI, y = HDI)) + geom_point(aes(color = Region, size =  HDI.Rank))
```

Exercise II
1. Re-create a scatter plot with CPI on the x axis and HDI on the y axis (as you did in the previous exercise).
```{r}
ggplot(data, aes(x = CPI, y = HDI)) + geom_point()
```

2. Overlay a smoothing line on top of the scatter plot using geom_smooth.
```{r}
ggplot(data, aes(x = CPI, y = HDI)) + geom_point() + geom_smooth()
```

3. Overlay a smoothing line on top of the scatter plot using geom_smooth, but use a linear model for the predictions. Hint: see ?stat_smooth.
```{r}
ggplot(data, aes(x = CPI, y = HDI)) + geom_point() + geom_smooth(method = "lm")
```

4. Overlay a smoothing line on top of the scatter plot using geom_line. Hint: change the statistical transformation.
```{r}
ggplot(data, aes(x = CPI, y = HDI)) + geom_point() + geom_line(stat = "smooth", method = "loess")
```

BONUS: Overlay a smoothing line on top of the scatter plot using the default loess method, but make it less smooth. Hint: see ?loess.
```{r}
ggplot(data, aes(x = CPI, y = HDI)) + geom_point() + geom_smooth(span = .4)
```

Exercise III
1. Create a scatter plot with CPI on the x axis and HDI on the y axis. Color the points to indicate region.
```{r}
ggplot(data, aes(x = CPI, y = HDI, color = Region)) + geom_point()
```

2. Modify the x, y, and color scales so that they have more easily-understood names (e.g., spell out “Human development Index” instead of “HDI”).
```{r}
ggplot(data, aes(x=CPI,y=HDI, color=Region)) + geom_point() + labs(x="Corruption Perception Index", y="Human Development Index") + scale_color_hue(name="Regions", labels=c("Americas", "Asia Pacific", "East EU Central Asia", "EU West Europe", "Middle East North Africa", "Sub-Saharan Africa"))
```

3. Modify the color scale to use specific values of your choosing.
```{r}
ggplot(data, aes(x=CPI,y=HDI, color=Region)) +geom_point() + labs(y="Human development index", x="Corruption perception index") + scale_color_manual(labels=c("Americas", "Asia Pacific", "Western Europe", "Eastern and Central Asia", "Middle East and Northern Africa", "Sub-Saharan Africa"), values=c("red", "orange", "yellow","green","blue", "purple"))
```



